When are Fuzzy Extractors Possible?

### 2014-07-02 trunk/info-bounds/FuzzyExtPossibility.tex
minor modifications to level proof

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
Let $\epsilon>0$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=k,..., n+\log 1/\epsilon$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-n}/\epsilon$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{lemma}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log 1/\delta - \log 1/\epsilon -\log n$.\bnote{come back and correct this}
\end{lemma}
\begin{proof}
We begin by arguing correctness.  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-n}\epsilon$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.  Now consider the case when $\Pr[W=w]> 2^{-n}\epsilon$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

We now argue security.  First note that the total weight of points whose probability is less than $2^{-n}\epsilon$ is at most $\epsilon$~(there are at most $2^n$ points in the distribution).  That is, $\sum_{w | \Pr[W=w]\le 2^{-n}\epsilon}\Pr[W = w] \le \epsilon$.  Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
-\log\left( \epsilon + (1-\epsilon)2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on $\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\Pr[W=w | \sketch(W)]$.
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&= \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&=\frac{ \expe_{i | k\le i \le n+\log 1/\epsilon} \left(2^{-i}*|B_{t, i, max}|\right)}{\delta}\\
%&=\delta \sum_{i | k\le i \le n+\log 1/\epsilon} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
\end{align*}
Now consider an adversary that receives $i$ as input, in the oracle setting, the best strategy is to guess a point that has the most weight in that layer.  The success of this adversary is at most $2^{-i}|B_{t,i, max}|$.  Note there are $n-k+\log 1/\epsilon$ outcomes for $i$ so the overall success of such an adversary is at most $n-k+\log 1/\epsilon$ better than an adversary without such input.  This allows us to conclude that 
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) &= \frac{(n-k+\log 1/\epsilon) 2^{-\Hfuzz(W)}}{\delta}.
\end{align*}
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\epsilon+\frac{(1-\epsilon)(n-k+\log1/\epsilon)2^{-\Hfuzz(W)}}{\delta}\right).
\end{align*}
Setting $\epsilon = 2^{-k}$ yields
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(k+(1-2^{-k})(n)2^{-\Hfuzz(W)/\delta}\right)\\
&\ge -\log \min\{k, (1-2^{-k}) n2^{-\Hfuzz(W)}/\delta\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-k}) - 1\\
&\ge \Hfuzz(W) - \log n + \log \delta - 2\\
\end{align*}

\end{proof}

>>>>

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

Before describing the bounds obtained by \consref{cons:leveling} we will extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = |B_{t, i, max}| /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
We begin by arguing correctness.  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is trivial.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} = \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).  That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.  Let $1_{\text{low prob}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low prob}}=1] * 1 + \Pr[1_{\text{low prob}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)\\
-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low prob}} = 0)}\right)
\end{align*}
We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.  An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.  That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
\end{align}
For the remainder of the proof, we seek a bound on \[\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
\end{align*}
Setting $\ell = m$ yields
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the whole quantity is negative~(and entropy is non-negative).
\end{proof}
